MINOS Handover Plots

### 2023-03-01 minos/validation/handovers.Rmd
Added some more variable definitions to some makefile targets. Also added titles and axis labels to the handover plots

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')
```

@@

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

@@

raw.phealth2 <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted')

raw.phealth.check <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

base.phealth.check <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, 
   raw.phealth.check, base.phealth.check, phealth2)
```

>>>>

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Income')

@@

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('Income')

@@

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12')

@@

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('SF12')
```

@@

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

@@

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Proportion') +
  xlab('Year') +
  ylab('Proportion')

@@

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
  xlab('Year') +
  ylab('Count')

@@

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Proportion') +
  xlab('Year') +
  ylab('Proportion')

@@

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness', subtitle = 'Counts by level') +
  xlab('Year') +
  ylab('Count')

@@

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness', subtitle = 'Proportion') +
  xlab('Year') +
  ylab('Proportion')

@@

# Now plot
ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Nutrition Quality', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Nutrition Quality')

@@

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Nutrition Quality', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('Nutrition Quality')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')

@@

raw.phealth2 <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('Average')

#raw.phealth.check <- raw.dat %>% 
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

#base.phealth.check <- base.dat %>%
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
#rm(raw.phealth.check, base.phealth.check)
```
